---
title: "Dixon_Homework2_Q3"
author: "Jerome Dixon"
date: "2/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

3. A researcher is interested in developing a statistical learning tool for antibiotic success
rates for a resistant strain of bacteria. Since this is a very dangerous strain care needs to
be taken to use the minimum number of petri dishes with the bacteria. It is assumed that
a priori that the success rate is 50-50 with probability of no success is zero as well as
probability of full success is zero.

a. What is a reasonable prior distribution?

Beta = (5,5)


b. The following sequence of success rates in petri dishes 𝑋 =
1,0,1,0,1,1,1,1,0,1,0,0,1,0,0,1,0,1,1,1,0.


c. What is the posterior distribution once the first observation has been observed?

```{r}

n = 1
bernoulli_success = 1

posterior_alpha1 <- 5 + bernoulli_success
posterior_beta1 <- 5 + n - bernoulli_success


posterior_distribution_n1 = beta(posterior_alpha1, posterior_beta1)


posterior_distribution_n1


```

d. What is the posterior distribution once the first two observations have been
observed?

```{r}

n = 2
bernoulli_success = 1

posterior_alpha2 <- 5 + bernoulli_success
posterior_beta2 <- 5 + n - bernoulli_success


posterior_distribution_n2 = beta(posterior_alpha2, posterior_beta2)


posterior_distribution_n2


```

e. What is the posterior distribution once the first three observations have been
observed?

```{r}

n = 3
bernoulli_success = 2

posterior_alpha3 <- 5 + bernoulli_success
posterior_beta3 <- 5 + n - bernoulli_success


posterior_distribution_n3 = beta(posterior_alpha3, posterior_beta3)


posterior_distribution_n3


```

f. Continue this process for all of the observations and create 95% credible intervals
at each step.

```{r}

test <- c(1,0,1,0,1,1,1,1,0,1,0,0,1,0,0,1,0,1,1,1,0)
X1 <- seq(0, 1, by=0.01)

n = 21
bernoulli_success = 12
theta <- X1

likelihood = function(n, bernoulli_success, theta){
  return(theta^bernoulli_success*(1-theta)*(n - bernoulli_success)) }

plot(theta, likelihood(n,bernoulli_success, theta))


```


g. At which step did the 95% credible interval go completely above 0.5?

At Step 19 it crosses .5